Word learning at the semantics pragmatics interface

### 2020-04-20 paper/supplementary_material.Rmd
update supplement

---
title: "Word learning at the semantics pragmatics interface"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler and Michael C. Frank"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age. As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning. In Experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge. In a second experiment, we show that children make inferences about word meanings based on common ground. In a third experiment, we find that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.

Next, we introduce a computational framework which we use to formalize the process of how the inferences are integrated. As a part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. We then use the our modelling framework to ask which of these information sources are necessary to predict children's responses in Experiment 3.

In the final section, we turn to the process by which information is integrated. We contrast the process of rational Bayesian inference we introduced in our model with a biased integration process in which one type of inference is given more weight. As part of this, we also explore alternative ways to think about developmental change in the integration process.

@@

The first experiment tested the so called mutual exclusivity inference in children between 2 and 5 years of age. The general phenomena is that when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g. @markman1988children]. A range of explanations have been put forward for the cognitive basis of this inference [see @lewis2020-me for a discussion]. Here, we treat the mutual exclusivity inference as pragmatic [e.g. @clark1987principle]. The inference process is specified in the model below.

The first goal of this experiment was to quantify developmental change in the age range tested. The second goal was to test the role of semantic knowledge [cf. @lewis2020-me]. The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object. That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object. To test this, we systematically varied the familiar object that were presented alongside the novel object.

The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository and opening the file `experiments/ex1_me.html`.

@@

The experiment was presented as an interactive picture book on a tablet computer [@frank2016using]. Figure \@ref(fig:fig1)A shows the general setup. Children saw an animal standing on a little hill between two tables. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests. Each experiment started with two training trials in which the speaker requested known objects (car and ball).

@@

```{r fig1,echo = F, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
knitr::include_graphics("../figures/method_overview.png")
```

Each child completed 12 trials, each with a different familiar and a different novel object. Familiar objects were selected to vary along the dimension of how likely children were to know the word for each object. This including objects that most 2-year-olds could name (e.g. a duck) as well as objects that only very few 5-year-olds could name (e.g. a pawn). The selection was based on age of acquisition ratings from Kuperman and colleagues [-@kuperman2012age]. While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned. Figure \@ref(fig:fig2)A shows the objects used in the experiment. We induced this variation to estimate the role of semantic knowledge in a mutual exclusivity inference.

@@

```{r table1, echo=T}
chance_me <- me_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

@@

As a first step, we evaluated whether children made a mutual exclusivity inference. For this analysis, we aggregated participants' responses across familiar objects. We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that children chose the novel object more often than expected by chance (50% correct). Table \@ref(tab:table1) shows that all age groups made the inference.

```{r, echo=T}
# prior_me <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")
# 
# 
# bm_me2 <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")

@@

```{r}
fixef_me <- as_tibble(fixef(bm_me), rownames = "term")

@@

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent. The priors we used were `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects.  The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.

The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. To assess the variability accross objects, we compared the fit of the above model to a model lacking `object` as a random effect. Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights. The WAIC score is an indicator of the model’s predictive accuracy for out of sample data; model’s with lower scores are preferred. WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data. The model including object provided a much better fit compared to the model lacking it (see Table \@ref(tab:table2)). Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and illustrates the substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory. Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept. The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the strength  of the mutual exclusivity inference depended on age as well as the familiar object.

```{r table2, echo=T}

@@

me_comp <- tibble(
  Model = c("with object as RE", "without object as RE"),
  WAIC = round(c(me_waic$loos$bm_me$estimates["waic","Estimate"],me_waic$loos$bm_me2$estimates["waic","Estimate"]),2),
  SE = round(c(me_waic$loos$bm_me$estimates["waic","SE"],me_waic$loos$bm_me2$estimates["waic","SE"]),2),
  weight = round(c(me_weights[1],me_weights[2]))
)

@@

```{r fig2, include = T, fig.align = "center", fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition. B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution. Dots show individual datapoints. Lighter colors indicate later rated age of acquisition. Dotted line indicates a level of performance expected by chance. C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
```

@@

The general setup was the same as in Experiment 1. The speaker was positioned between the tables. There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second novel object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B). The positioning of the novel object in the beginning of the experiment as well as the location the speaker turned to first was counterbalanced. Children received five trials, each with a different pair of novel objects. We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.

@@

```{r table3, echo=T}
chance_prior <- prior_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf,2), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

@@

```{r, echo=T}
# prior_cg <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = prior_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_cg,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_cg.rds")

@@

Experiment 3 combined the procedures from Experiment 1 and 2. As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but also the role that each object (novel and familiar) had played in the preceding interaction. Combining the two procedures created two conditions: In the *congruent* condition, the novel object was also the object that was new to the speaker. In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent. In the *incongurent condition*, the familiar object was new to the speaker. Int his case, the two inferences pointed to different objects. The main focus of the overall study was to model how children integrate and balance these different information sources. We investigate this question in depth in the [modelling](#model) section below. Here, we limit the discussion to whether children differentiated between the two conditions.

@@

Experiment 3 followed the same procedure as Experiment 2 but involved the same objects as Experiment 1. In the beginning, one table was empty while there was an object (novel or familiar) on the other one. After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel). Next, the speaker re-appeared and made the usual request.

@@

Participants received up to 12 test trials, six in each condition, each with a different familiar and novel object. Familiar objects were the same as in Experiment 1. The positioning of the objects on the tables and the location the speaker first turned to were counterbalanced. Participants could stop the experiment after six trials (three per condition). If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per cell.

@@

All results are reported from the perspective of the mutual exclusivity inference (`correct` in the model formula below). In the incongruent condition, high proportions speak to a mutual exclusivity inference and low proportion for a common ground inference. In the congruent condition, both inferences pointed in the same direction. The focus of this experiment was on information integration and we therefore did not compare the performance to chance.

```{r, echo=T}

@@

```{r}
fixef_comb <- as_tibble(fixef(bm_comb), rownames = "term")

@@

```{r table4, echo=T}

@@

comb_comp <- tibble(
  Model = c("with object as RE", "without object as RE"),
  WAIC = round(c(comb_waic$loos$bm_comb$estimates["waic","Estimate"],comb_waic$loos$bm_comb2$estimates["waic","Estimate"]),2),
  SE = round(c(comb_waic$loos$bm_comb$estimates["waic","SE"],comb_waic$loos$bm_comb2$estimates["waic","SE"]),2),
  weight = round(c(comb_weights[1],comb_weights[2]))
)

@@

```{r fig3, include = T, fig.align = "center", fig.cap = "Proportion of choosing the object that was new to the speaker by age. Dots show the mean response for each participant. The solid black line shows the developmental trajectory based on the mean of the model posterior distribution. Lighter lines show 200 random draws from the posterior distribution to depict uncertainty. Dotted line indicates a level of performance expected by chance.", fig.width=12, fig.height = 4}
ggarrange(plot_cg, plot_comb,  labels = c("A","B"), nrow = 1, widths = c(1,2))
```

@@

The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate. Experiment 1 showed that children of all age groups make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented. Experiment 2 showed that children are sensitive to the common ground manipulation we implemented and that this inference increases with age. Finally, Experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another. In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when inferences are combined with one another.

# Models

@@

$$
P_{L}(r \mid u)\propto P_{S}(u \mid r) \cdot P(r \mid \rho_i) \\ 
P_{S}(u \mid r)\propto P(r\mid u) ^{\alpha_i} \\
P(r\mid u) \propto \mathcal{L}(u, r \mid \theta_{ij})
$$

Our model describes a listener ($P_L$) reasoning about the referent referred to by a speaker's ($P_S$) utterance. This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$. This prior probability is a function of the common ground $\rho$ shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later. We assume that the degree to which interactions around objects are integrated into the common ground (and thus change the prior probability of those objects) depends on the child's age $i$.

To decide between referents, the listener reasons about what a rational speaker would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$. In particular, we take $\alpha$ to be a function of the child's age $i$.

The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
  Following @frank2014inferring, we use an implicit uniform prior over referents in the literal listener.
] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We parameterize the listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1. $\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene. Each of the novel words are assumed to have semantic knowledge of 0. For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
  One could also define $\theta$ to directly denote the probability of selecting the familiar~vs.~unfamiliar referent. The model behavior would be the same except for a translation of this parameter. We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete uncertainty.
] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.

The model with each data-analytic parameter represented explicitly in $\{, \}s$ is:

$$
P_{L}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) \\ 
P_{S}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} \\
P(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})
$$

@@

\begin{tikzpicture}
%% RSA nodes and data
\node[obs](data_comb){$d^{CM}_{ijk}$};
\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{ij}$};
\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};

>>>>

---
title: "Word learning at the semantics pragmatics interface"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

The goal of this study is to investigate the integration of information during word learning in children between 2 and 5 years of age. As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning. In [Experiment 1](#experiment-1-mutual-exclusivity), we show that children make a so-called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge. In [Experiment 2](#experiment-2-common-ground), we show that children make inferences about word meanings based on common ground. In [Experiment 3](#experiment-3-combination), we show that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.

[Next](#cognitive-models), we introduce a computational cognitive model (**integration model**) in which we formalize the process of how information sources are integrated. As part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. We then use the our modelling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.

In the [final section](#explanation), we turn to the process by which information is integrated. We contrast the process of Bayesian inference we introduced in our model with a biased integration process in which some inforamtion sources are weighted as more important. As part of this, we also explore alternative ways to think about developmental change in the integration process.

@@

The first experiment tested the so-called mutual exclusivity inference in children between 2 and 5 years of age. The general inference can be described as follows: when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g. @markman1988children]. A range of explanations have been put forward for the cognitive basis of this inference [see @lewis2020-me for a discussion]. Here, we treat mutual exclusivity as a pragmatic phenomenon [e.g. @clark1987principle]. The inference process is specified in the model below.

The first goal of this experiment was to quantify developmental change in the age range tested. The second goal was to test the role of semantic knowledge [cf. @lewis2020-me]. The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object presented alongside the novel object. That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object. To test this, we systematically varied the familiar object that were presented alongside the novel object.

The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository (https://github.com/manuelbohn/spin) and opening the file `experiments/ex1_me.html`.

@@

The experiment was presented as an interactive picture book on a tablet computer [@frank2016using]. Figure \@ref(fig:fig1)A shows the general setup. Children saw an animal standing on a little hill between two tables. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to talk to the child and make requests. Each experiment started with two training trials in which the speaker requested known objects (car and ball).

@@

```{r fig1,echo = F,  fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
knitr::include_graphics("../figures/method_overview.png")
```

Each child completed 12 trials, each with a different familiar and a different novel object. Familiar objects were selected to vary along the dimension of how likely children were to know the word for each object. This including objects that most 2-year-olds can name (e.g. a duck) as well as objects that only very few 5-year-olds can name (e.g. a pawn). The selection was based on age of acquisition ratings from Kuperman and colleagues [-@kuperman2012age]. While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned. Figure \@ref(fig:fig2)A shows the words and objects used in the experiment. We induced this variation to estimate the role of semantic knowledge in a mutual exclusivity inference.

@@

```{r table1, echo=F}
chance_me <- me_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

@@

As a first step, we evaluated whether children made a mutual exclusivity inference. For this analysis, we aggregated participants' responses across familiar objects. We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes Factor (BF) in favor of the hypothesis that children chose the novel object more often than expected by chance (50%). Table \@ref(tab:table1) shows that all age groups made the inference.

```{r, echo=F}
# prior_me <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")
# 
# 
# bm_me2 <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = me_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_me,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_me.rds")

@@

```{r, cache = T}
fixef_me <- as_tibble(fixef(bm_me), rownames = "term")

@@

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent. The priors we used were $\text{Gaussian}(0,5)$ for fixed (population level) effects and $\text{Cauchy}(0,1)$ for standard deviations of random effects. The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.

The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. To assess the variability accross objects, we compared the fit of the above model to a model lacking `object` as a random effect. Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights. The WAIC score is an indicator of the model’s predictive accuracy for out of sample data; model’s with lower scores are preferred. WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data. The model including object provided a much better fit compared to the model lacking it (see Table \@ref(tab:table2)). Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and illustrates the substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory. Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept (i.e. mutual exclusivity inference at age 2.00). The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the strength of the mutual exclusivity inference depended on age as well as the familiar object.

```{r table2, echo=F, cache = T}

@@

me_comp <- tibble(
  Model = c("with object as RE", "without object as RE"),
  WAIC = round(c(me_waic$loos$bm_me$estimates["waic","Estimate"],me_waic$loos$bm_me2$estimates["waic","Estimate"]),2),
  SE = round(c(me_waic$loos$bm_me$estimates["waic","SE"],me_waic$loos$bm_me2$estimates["waic","SE"]),2),
  weight = format(round(c(me_weights[1],me_weights[2]),2), nsmall = 2)
)

@@

```{r fig2, include = T, fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition. B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution. Dots show individual datapoints. Lighter colors indicate later rated age of acquisition. Dotted line indicates a level of performance expected by chance. C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
```

@@

The general setup was the same as in Experiment 1. The speaker was positioned between the tables. There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second novel object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B). The positioning of the novel object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced. Children received five trials, each with a different pair of novel objects. We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.

@@

```{r table3, echo=F}
chance_prior <- prior_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf,2), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

@@

```{r, echo=F}
# prior_cg <- c(prior(normal(0, 5), class = Intercept),
#            prior(normal(0, 5), class = b),
#            prior(cauchy(0, 1), class = sd))
# 
# 
# bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = prior_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           prior = prior_cg,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_cg.rds")

@@

Experiment 3 combined the procedures from Experiment 1 and 2. As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but also the role that each object (novel and familiar) had played in the preceding interaction. Combining the two procedures created two alignment conditions: In the *congruent condition*, the novel object was also the object that was new to the speaker. In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent. In the *incongurent condition*, the familiar object was new to the speaker. In this case, the two inferences pointed to different objects. The main focus of the overall study was to model how children integrate and balance these different information sources. We investigate this question in depth in the [modelling](#cognitive-models) section below. Here, we limit the discussion to whether children differentiated between the two conditions.

@@

Experiment 3 followed the same procedure as Experiment 2 but involved the same objects as Experiment 1 (Figure \@ref(fig:fig1)C). In the beginning, one table was empty while there was an object (novel or familiar) on the other one. After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel). Next, the speaker re-appeared and made the usual request.

@@

Participants received up to 12 test trials, six in each condition, each with a different familiar and novel object. Familiar objects were the same as in Experiment 1. The positioning of the objects on the tables, the speaker and the location the speaker first turned to were counterbalanced. Participants could stop the experiment after six trials (three per condition). If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per age group (2-, 3- and 4-year-olds).

@@

All results are reported from the perspective of the mutual exclusivity inference (`correct` in the model formula below). In the incongruent condition, high proportions speak to a mutual exclusivity inference and low proportion to a common ground inference. In the congruent condition, both inferences pointed in the same direction. The focus of this experiment was on information integration and we therefore did not compare the performance to chance.

```{r, echo=F}

@@

```{r, cache = T}
fixef_comb <- as_tibble(fixef(bm_comb), rownames = "term")

@@

```{r table4, echo=F, cache = T}

@@

comb_comp <- tibble(
  Model = c("with object as RE", "without object as RE"),
  WAIC = round(c(comb_waic$loos$bm_comb$estimates["waic","Estimate"],comb_waic$loos$bm_comb2$estimates["waic","Estimate"]),2),
  SE = round(c(comb_waic$loos$bm_comb$estimates["waic","SE"],comb_waic$loos$bm_comb2$estimates["waic","SE"]),2),
  weight = format(round(c(comb_weights[1],comb_weights[2]),2), nsmall = 2)
)

@@

```{r fig3, include = T,  fig.cap = "Proportion of choosing the object that was new to the speaker by age. Dots show the mean response for each participant. The solid black line shows the developmental trajectory based on the mean of the model posterior distribution. Lighter lines show 200 random draws from the posterior distribution to depict uncertainty. Dotted line indicates a level of performance expected by chance.", fig.width=12, fig.height = 4}
ggarrange(plot_cg, plot_comb,  labels = c("A","B"), nrow = 1, widths = c(1,2))
```

@@

The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate. Experiment 1 showed that children of all age groups make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on children's semantic knowledge. Experiment 2 showed that children are sensitive to the common ground manipulation we implemented and that the sensitivity to common ground increases with age. Finally, Experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another. In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when inferences are combined with one another.

# Cognitive models

@@

\begin{equation}
P_{L_1}(r \mid u)\propto P_{S_1}(u \mid r) \cdot P(r \mid \rho_i) \\ 
P_{S_1}(u \mid r)\propto P_{L_0}(r\mid u) ^{\alpha_i} \\
P_{L_0}(r\mid u) \propto \mathcal{L}(u, r \mid \theta_{ij})
(\#eq:rsabasic)
\end{equation}

Our model describes a listener ($L_1$) reasoning about the referent referred to by a speaker's ($S_1$) utterance. This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$. This prior probability is a function of the common ground $\rho$ shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later. We assume that the degree to which interactions around objects are integrated into the common ground (and thus change the prior probability of those objects) depends on the child's age $i$.

To decide between referents, the listener ($L_1$) reasons about what a rational speaker ($S_1$) would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$. In particular, we take $\alpha$ to be a function of the child's age $i$.

The informativity of each utterance is given by imagining which referent a literal listener ($L_0$), who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
  Following @frank2014inferring, we use an implicit uniform prior over referents in the literal listener.
] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We parameterize the listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1. $\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene. Each of the novel words are assumed to have semantic knowledge of 0. For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
  One could also define $\theta$ to directly denote the probability of selecting the familiar~vs.~unfamiliar referent. The model behavior would be the same except for a translation of this parameter. We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete uncertainty.
] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.

The model with each data-analytic parameter represented explicitly in $\{ \}$ is:

\begin{equation}
P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) \\ 
P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} \\
P_{L_0}(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})
(\#eq:rsafull)
\end{equation}

@@

\resizebox{1\textwidth}{!}{

\begin{tikzpicture}

\node[obs](data_comb){$d^{Ex3}_{ijk}$};
\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{Ex1}_{ij}$};
\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{Ex2}_{i}$};

\node[det, above=of data_me](L1_me){$L_1'$};
\node[det, above=of data_comb](L1_comb){$L_1$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};
